### 2016-06-28 lineups.Rnw
couple quick paragraphs

@@

>>>>

<<results1, echo = FALSE>>=
lus_res_long <- read.csv("Data/June_estimates_from_lineups.csv", stringsAsFactors = FALSE)

@

@@

The strong influence of the inclusion of $\beta_4$ in model 3 has made any comparison between model 1 and model 3 impossible. The $\beta_4$ estimate is always significantly greater than zero in fitted models that converged. Thus, $\beta_4$ should have been included from the beginning.
% at end of param est we know that model m3 is useless. m3 messes with structure of m1. should have been in cluded in all of the models. nice & important but doesn't help for lineup study

%  results from the the pilot study. how do estimates combine with pilot study ? have 10 non-m3 ones that are good. also want to see that m1 v m3 is way worse than m1 v m2. now have a reason for m1 v m3 is so bad. m1 v m3 ids should be NO GOOD.
